### 2013-12-17 poster/poster.tex
added authors and logo
a1

\documentclass[a0,portrait]{a0poster}

@@

\usepackage{times} % Use the times font
\usepackage{palatino} % Uncomment to use the Palatino font

@@

\begin{minipage}[b]{0.75\linewidth}
\veryHuge \color{NavyBlue} \textbf{Hierarchical Controller Architecture} \color{Black}\\ % Title
\Huge\color{NavyBlue}\text{in Software Defined Networks}\\[1cm] % Subtitle
\huge \textbf{Author1 \& Author2}\\[0.5cm] % Author(s)
%\huge University and Department Name\\[0.4cm] % University/organization
%\Large \texttt{john@LaTeXTemplates.com} --- 1 (000) 111 1111\\
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\includegraphics[width=20cm]{logo.png}\\
\end{minipage}

\vspace{1cm} % A bit of extra whitespace between the header and poster content

@@

\begin{figure}[H]
\centering
\includegraphics[scale=2]{hierarchy}
\caption{Hierarchical arrangement of controllers}
\label{fig:hierarchy}
\end{figure}

@@

%\begin{center}\vspace{1cm}
%\includegraphics[width=0.8\linewidth]{msg}
%\captionof{figure}{\color{Green} Per flow communication overhead}
%\label{fig:msg}
%\end{center}\vspace{1cm}
\begin{figure}[H]
\centering
\includegraphics[scale=1]{msg}
\caption{Per flow communication overhead}
\label{fig:msg}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}  
    \subfigure[Path length]{\label{fig:path}\includegraphics[scale=0.75]{path.png}} 
    \subfigure[Maximum link utilization]{\label{fig:util}\includegraphics[scale=0.75]{util.png}} 
  \end{center}
\caption{Application performance}
\end{figure}

@@

\color{SaddleBrown}
\subsection*{SOURCE CODE}
\color{DarkSlateGray}
https://github.com/MugiwaraLuffy/ACN/

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

>>>>

\documentclass[portrait,a1]{a0poster}

@@

%x\usepackage{times} % Use the times font
\usepackage{palatino} % Uncomment to use the Palatino font

@@

\begin{minipage}[b]{0.75\linewidth}
\Huge \color{NavyBlue} \textbf{Hierarchical Controller Architecture} \color{Black}\\ % Title
\Huge\color{NavyBlue}\text{in Software Defined Networks}\\[1cm] % Subtitle
\Large \textbf{Author1 \& Author2}\\[0.5cm] % Author(s)
%\huge University and Department Name\\[0.4cm] % University/organization
%\Large \texttt{john@LaTeXTemplates.com} --- 1 (000) 111 1111\\
\end{minipage}
%

\vspace{-1cm} % A bit of extra whitespace between the header and poster content

@@

\begin{figure}[H]
\centering
\includegraphics[scale=1.9]{hierarchy}
\caption{Hierarchical arrangement of controllers}
\label{fig:hierarchy}
\end{figure}

@@

%\begin{center}\vspace{1cm}
%\includegraphics[width=0.8\linewidth]{msg}
%\captionof{figure}{\color{Green} Per flow communication overhead}
%\label{fig:msg}
%\end{center}\vspace{1cm}
\begin{figure}[H]
\centering
\includegraphics[scale=01]{msg}
\caption{Per flow communication overhead}
\label{fig:msg}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}  
    \subfigure[Path length]{\label{fig:path}\includegraphics[scale=0.55]{path.png}} 
    \subfigure[Maximum link utilization]{\label{fig:util}\includegraphics[scale=0.55]{util.png}} 
  \end{center}
\caption{Application performance}
\end{figure}

@@

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------
\color{SaddleBrown}
\section*{RESOURCES}
\color{DarkSlateGray}
\section*{Source Code}
https://github.com/MugiwaraLuffy/ACN/
\nocite{*} % Print all references regardless of whether they were cited in the poster or not
%\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib
